Understanding Expectation Formation from Probabilistic Surveys

### 2019-06-18 slides/ExpSlides.tex
seperate MP and non-MP shocks for IRF. Looking into sub period consistent with coibion to replicate their results

\begin{frame}{Forecasting errors IR to  shocks including monetary policy}

@@

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks_nmp.png} 
\end{figure}

@@

\begin{frame}{Disagreements IR to  shocks including monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks.png} 
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ashocks_nmp.png} 
\end{figure}

@@

\begin{frame}{Uncertainty IR to shocks including monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ashocks.png} 
\end{figure}

>>>>

\begin{frame}{Forecasting errors IR to monetary policy shocks}

@@

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ab_ashocks_nmp.png} 
\end{figure}

@@

\begin{frame}{Disagreements IR to  monetary policy shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ab_ashocks.png} 
\end{figure}

@@

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ab_ashocks_nmp.png} 
\end{figure}

@@

\begin{frame}{Uncertainty IR to monetary policy shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ab_ashocks.png} 
\end{figure}
